*Supplementary Material*

### 2022-02-17 ms/manuscript.Rmd
Update MS

There are differences between pteridocat and PPGI, mostly at the genus level.
In the time since PPGI was published, several new genera have been published.
Furthermore, multiple genera included in PPGI were known to be non-monophyletic and included on a tentative basis [@PteridophytePhylogenyGroupI2016].
Pteridocat includes newly published genera and some genera that were not recognized by PPGI.
Differences between pteridocat and PPGI are summarized in Table S1.

>>>>

There are differences between pteridocat and PPGI, mostly at the genus level.
In the time since PPGI was published, several new genera have been published.
Furthermore, multiple genera included in PPGI were known to be non-monophyletic and included on a tentative basis [@PteridophytePhylogenyGroupI2016].
Pteridocat includes newly published genera and some genera that were not recognized by PPGI as well as nothogenera, which were not included in PPGI [@Liu2020a].
Differences between pteridocat and PPGI are summarized in `r s_table("genera_diff")`.

### 2022-02-17 ms/si.Rmd
Update MS

tar_load(
	c(
		sanger_alignment_tbl,
		sanger_sampling,
		sanger_accessions_selection,
		plastome_tree,
		plastid_tree_dated,
		fossil_calibration_tips),
	store = ftol_cache
)

# Targets from MS workflow
tar_load(
	c(
		gb_species_by_year,
		ref_files,
		other_dates,
		du_dates_all,
		family_stem_ages,
		fossil_ferns_raw
	),
	store = here::here("_targets")
)
```

@@

@@

**`r s_table("fossils")`**. Fossils used as calibration points for molecular dating (`r result_file(s_table("fossils"), "csv")`). "n_fos" is the fossil ID number used in our fossil database (https://github.com/pteridophy/fossils). "minimum_age" (Ma) is the age used for calibration; "lower" is the lower limit of the oldest stratigraphic age for the fossil; "upper" is the upper limit of the oldest stratigraphic age for the fossil.

>>>>

tar_load(
	c(
		sanger_alignment_tbl,
		sanger_sampling,
		sanger_accessions_selection,
		plastome_tree,
		plastid_tree_dated,
		fossil_calibration_tips,
		ppgi_taxonomy),
	store = ftol_cache
)

# Targets from MS workflow
tar_load(
	c(
		accepted_species,
		gb_species_by_year,
		ref_files,
		other_dates,
		du_dates_all,
		family_stem_ages,
		fossil_ferns_raw
	),
	store = here::here("_targets")
)
```

@@

```{r genera-diff}

# FIXME: need to update ppgi csv file
# Add one missing nothogenus
ppgi_taxonomy_mod <-
	bind_rows(
		ppgi_taxonomy,
		tibble(
			genus = "Phlebosia",
			notes = "Nothogenus"
		)
	)

# Verify that all accepted genera are accounted for
accepted_species %>%
	count(genus, name = "n_species") %>%
	anti_join(select(ppgi_taxonomy_mod, genus, notes)) %>%
	verify(nrow(.) == 0, success_fun = success_logical)

# Make table of Pteridocat genera not in PPGI
pteridocat_not_in_ppgi <-
accepted_species %>%
	count(genus, name = "n_species") %>%
	left_join(select(ppgi_taxonomy_mod, genus, notes), by = "genus") %>%
	assert(not_na, notes) %>%
	assert(is_uniq, genus) %>%
	filter(notes != "original PPGI 2016") %>%
	transmute(
		diff = "Pteridocat not in PPGI",
		genus,
		n_species,
		note = notes
	)

# Make table of PPGI genera not in Pteridocat
ppgi_not_in_pteridocat <-
ppgi_taxonomy_mod %>%
	filter(notes == "original PPGI 2016",
				 class == "Polypodiopsida") %>%
	anti_join(accepted_species, by = "genus") %>%
	count(genus) %>%
	transmute(
		diff = "PPGI not in Pteridocat",
		genus,
		# FIXME: need to add n species from PPGI and note
		n_species = NA,
		note = NA
	)

genera_diff_table <- 
	bind_rows(pteridocat_not_in_ppgi, ppgi_not_in_pteridocat)

write_csv(genera_diff_table, result_file(s_table("genera_diff"), "csv"))
```

**`r s_table("genera_diff")`**.
Differences in genera included as accepted in Pteridocat taxonomic database (https://github.com/pteridophy/pteridocat) vs. @PteridophytePhylogenyGroupI2016 (`r result_file(s_table("genera_diff"), "csv") %>% fs::path_file()`).
"diff" is type of difference (Pteridocat genus not in PPGI or PPGI genus not in Pteridocat).
"n_species" is the number of accepted species in each genus in the system that includes the genus.
References in "notes" column provided at end of Supplementary Materials.

@@

**`r s_table("fossils")`**.
Fossils used as calibration points for molecular dating (`r result_file(s_table("fossils"), "csv") %>% fs::path_file()`).
"n_fos" is the fossil ID number used in our fossil database (https://github.com/pteridophy/fossils).
"minimum_age" (Ma) is the age used for calibration; "lower" is the lower limit of the oldest stratigraphic age for the fossil; "upper" is the upper limit of the oldest stratigraphic age for the fossil.
